---
title: "Unsere Wege"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    self_contained: false
knit: >-
  (function(inputFile, encoding) {
    inputFile <- normalizePath(inputFile);
    project_dir <- dirname(dirname(inputFile));
    output_dir <- file.path(project_dir, "Data", "3_Output");
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE);
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      output_file = "index.html",
      output_dir = output_dir
    )
  })
---

<style>
.track-stats {
  width: 100%;
  border-collapse: collapse;
  font-size: 13px;
}

.track-stats th {
  padding: 7px 8px;
  text-align: right;
  color: #65727d;
  font-size: 10px;
  font-weight: 700;
  letter-spacing: .055em;
  text-transform: uppercase;
  border-bottom: 1px solid #cfd7dd;
  white-space: nowrap;
}

.track-stats th:first-child,
.track-stats th:nth-child(2) {
  text-align: left;
}

.track-stats td {
  padding: 7px 8px;
  text-align: right;
  border-bottom: 1px solid #e2e7eb;
  white-space: nowrap;
}

.track-stats td:first-child,
.track-stats td:nth-child(2) {
  text-align: left;
}

.track-stats td.num {
  font-weight: 700;
}

.track-stats tr:last-child td {
  border-bottom: 0;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

# The dashboard reads CLEANED GPX files only.
# All route-specific cleaning is done by 01_Preprocess.R.
#
# Packages:
# install.packages(c(
#   "flexdashboard", "rmarkdown", "xml2",
#   "leaflet", "plotly", "htmltools"
# ))

required_packages <- c(
  "xml2",
  "leaflet",
  "plotly",
  "htmltools"
)

missing_packages <- required_packages[
  !vapply(
    required_packages,
    requireNamespace,
    logical(1),
    quietly = TRUE
  )
]

if (length(missing_packages) > 0) {
  stop(
    "Install required package(s): ",
    paste(
      missing_packages,
      collapse = ", "
    )
  )
}


input_rmd <- knitr::current_input(
  dir = TRUE
)

if (
  length(input_rmd) == 1 &&
  !is.na(input_rmd) &&
  nzchar(input_rmd)
) {
  script_dir <- dirname(
    normalizePath(input_rmd)
  )
} else {
  script_dir <- normalizePath(".")
}

project_dir <- if (
  basename(script_dir) == "Scripts"
) {
  dirname(script_dir)
} else {
  stop(
    "02_Dashboard.Rmd must be stored in the project's Scripts/ folder."
  )
}

intermediate_dir <- file.path(
  project_dir,
  "Data",
  "2_Intermediate"
)

output_dir <- file.path(
  project_dir,
  "Data",
  "3_Output"
)

dir.create(
  output_dir,
  recursive = TRUE,
  showWarnings = FALSE
)

manifest_file <- file.path(
  intermediate_dir,
  "UnsereWege_manifest.csv"
)

if (!file.exists(manifest_file)) {
  stop(
    paste0(
      "Preprocessed manifest not found. Run Scripts/01_Preprocess.R first: ",
      manifest_file
    )
  )
}

tz_local <- "Europe/Vienna"


# ============================================================
# 1. READ CLEANED GPX
# ============================================================

manifest <- utils::read.table(
  manifest_file,
  header = TRUE,
  sep = ";",
  dec = ".",
  quote = "\"",
  stringsAsFactors = FALSE,
  fileEncoding = "UTF-8",
  check.names = FALSE
)

manifest$date_local <- as.Date(
  manifest$date_local
)

manifest <- manifest[
  order(
    manifest$date_local,
    manifest$group,
    manifest$day_no
  ),
]

rownames(manifest) <- NULL

gpx_paths <- file.path(
  intermediate_dir,
  manifest$gpx_file
)

if (any(!file.exists(gpx_paths))) {
  stop(
    "Missing cleaned GPX file(s): ",
    paste(
      basename(
        gpx_paths[
          !file.exists(gpx_paths)
        ]
      ),
      collapse = ", "
    )
  )
}


read_clean_gpx <- function(i) {
  meta <- manifest[
    i,
  ]

  file <- file.path(
    intermediate_dir,
    meta$gpx_file
  )

  doc <- xml2::read_xml(file)

  p <- xml2::xml_find_all(
    doc,
    ".//*[local-name()='trkpt']"
  )

  time_utc <- as.POSIXct(
    xml2::xml_text(
      xml2::xml_find_first(
        p,
        "./*[local-name()='time']"
      )
    ),
    format = "%Y-%m-%dT%H:%M:%OSZ",
    tz = "UTC"
  )

  local_dates <- unique(
    as.Date(
      format(
        time_utc,
        tz = tz_local,
        format = "%Y-%m-%d"
      )
    )
  )

  if (
    length(local_dates) != 1 ||
    local_dates != meta$date_local
  ) {
    stop(
      "Cleaned GPX date does not match manifest: ",
      meta$gpx_file
    )
  }

  data.frame(
    source_track   = meta$day_id,
    group          = meta$group,
    group_label    = meta$group_label,
    day_no         = meta$day_no,
    day_id         = meta$day_id,
    display_day_id = meta$day_id,
    time_utc       = time_utc,
    date_local     = meta$date_local,
    date_label     = format(
      meta$date_local,
      "%d %b %Y"
    ),
    legend_label   = paste0(
      meta$day_id,
      " · ",
      format(
        meta$date_local,
        "%d %b %Y"
      )
    ),
    lon = as.numeric(
      xml2::xml_attr(
        p,
        "lon"
      )
    ),
    lat = as.numeric(
      xml2::xml_attr(
        p,
        "lat"
      )
    ),
    elevation = as.numeric(
      xml2::xml_text(
        xml2::xml_find_first(
          p,
          "./*[local-name()='ele']"
        )
      )
    ),
    stringsAsFactors = FALSE
  )
}


raw_points <- do.call(
  rbind,
  lapply(
    seq_len(nrow(manifest)),
    read_clean_gpx
  )
)

raw_points <- raw_points[
  order(
    raw_points$group,
    raw_points$day_no,
    raw_points$time_utc
  ),
]

rownames(raw_points) <- NULL


# ============================================================
# 2. DERIVED WALKING METRICS
#
# This is analysis, not cleaning:
# distance, smoothed elevation, ascent/descent, and break/active time.
# ============================================================

haversine <- function(lon1, lat1, lon2, lat2) {
  r <- 6371000

  p1 <- lat1 * pi / 180
  p2 <- lat2 * pi / 180
  dp <- (lat2 - lat1) * pi / 180
  dl <- (lon2 - lon1) * pi / 180

  a <- sin(dp / 2)^2 +
    cos(p1) * cos(p2) * sin(dl / 2)^2

  2 * r * asin(
    sqrt(
      pmin(
        1,
        a
      )
    )
  )
}


break_speed_kmh   <- 1
break_min_minutes <- 2
break_diameter_m  <- 60
break_vertical_m  <- 15


bbox_diameter_m <- function(lon, lat) {
  if (length(lon) < 2) {
    return(0)
  }

  lon_min <- min(lon)
  lon_max <- max(lon)
  lat_min <- min(lat)
  lat_max <- max(lat)
  lat_mid <- mean(
    c(
      lat_min,
      lat_max
    )
  )

  dx <- haversine(
    lon_min,
    lat_mid,
    lon_max,
    lat_mid
  )

  dy <- haversine(
    lon_min,
    lat_min,
    lon_min,
    lat_max
  )

  sqrt(
    dx^2 +
      dy^2
  )
}


detect_break_intervals <- function(d) {
  n <- nrow(d)

  if (n < 2) {
    return(
      logical(0)
    )
  }

  dt_h <- as.numeric(
    diff(
      d$time_utc
    ),
    units = "hours"
  )

  step_m <- haversine(
    d$lon[-n],
    d$lat[-n],
    d$lon[-1],
    d$lat[-1]
  )

  speed_kmh <- ifelse(
    dt_h > 0,
    step_m / 1000 / dt_h,
    Inf
  )

  low_speed <- speed_kmh <= break_speed_kmh
  is_break <- rep(
    FALSE,
    n - 1
  )

  i <- 1

  while (i <= n - 1) {
    if (!low_speed[i]) {
      i <- i + 1
      next
    }

    j <- i

    while (
      j < n - 1 &&
      low_speed[j + 1]
    ) {
      j <- j + 1
    }

    point_idx <- i:(j + 1)

    duration_min <- sum(
      as.numeric(
        diff(
          d$time_utc[point_idx]
        ),
        units = "mins"
      )
    )

    dz <- diff(
      d$ele_smooth[point_idx]
    )

    ascent_m <- sum(
      pmax(
        dz,
        0
      ),
      na.rm = TRUE
    )

    descent_m <- sum(
      pmax(
        -dz,
        0
      ),
      na.rm = TRUE
    )

    diameter_m <- bbox_diameter_m(
      d$lon[point_idx],
      d$lat[point_idx]
    )

    if (
      duration_min >= break_min_minutes &&
      diameter_m <= break_diameter_m &&
      ascent_m <= break_vertical_m &&
      descent_m <= break_vertical_m
    ) {
      is_break[i:j] <- TRUE
    }

    i <- j + 1
  }

  is_break
}


prepare_one_day <- function(d) {
  d <- d[
    order(
      d$time_utc,
      d$source_track
    ),
  ]

  n <- nrow(d)

  step_m <- c(
    0,
    haversine(
      d$lon[-n],
      d$lat[-n],
      d$lon[-1],
      d$lat[-1]
    )
  )

  dt_min <- c(
    0,
    as.numeric(
      diff(
        d$time_utc
      ),
      units = "mins"
    )
  )

  k <- min(
    9,
    n
  )

  if (k %% 2 == 0) {
    k <- k - 1
  }

  ele_smooth <- if (k >= 3) {
    stats::runmed(
      d$elevation,
      k = k,
      endrule = "median"
    )
  } else {
    d$elevation
  }

  dz <- c(
    0,
    diff(
      ele_smooth
    )
  )

  d$ele_smooth    <- ele_smooth
  d$step_m        <- step_m
  d$dt_min        <- dt_min
  d$gain_step_m   <- pmax(dz, 0)
  d$loss_step_m   <- pmax(-dz, 0)
  d$distance_km   <- cumsum(step_m) / 1000
  d$cum_ascent_m  <- cumsum(d$gain_step_m)
  d$cum_descent_m <- cumsum(d$loss_step_m)

  break_interval <- detect_break_intervals(
    d
  )

  interval_min <- if (n >= 2) {
    as.numeric(
      diff(
        d$time_utc
      ),
      units = "mins"
    )
  } else {
    numeric(0)
  }

  elapsed_min <- if (n >= 2) {
    as.numeric(
      difftime(
        d$time_utc[n],
        d$time_utc[1],
        units = "mins"
      )
    )
  } else {
    0
  }

  break_min <- sum(
    interval_min[
      break_interval
    ],
    na.rm = TRUE
  )

  active_min <- elapsed_min -
    break_min

  d$is_break_from_previous <- c(
    FALSE,
    break_interval
  )

  d$elapsed_h <- elapsed_min / 60
  d$break_h   <- break_min / 60
  d$active_h  <- active_min / 60

  d
}


points_split <- split(
  raw_points,
  raw_points$day_id
)

points <- do.call(
  rbind,
  lapply(
    points_split,
    prepare_one_day
  )
)

points <- points[
  order(
    points$group,
    points$day_no,
    points$time_utc
  ),
]

rownames(points) <- NULL


# ============================================================
# 3. DAY + GROUP SUMMARIES
# ============================================================

day_split <- split(
  points,
  points$day_id
)

days <- do.call(
  rbind,
  lapply(
    day_split,
    function(d) {
      data.frame(
        day_id        = d$day_id[1],
        display_day_id = d$display_day_id[1],
        day_no        = d$day_no[1],
        group         = d$group[1],
        group_label   = d$group_label[1],
        date_local    = d$date_local[1],
        date_label    = d$date_label[1],
        legend_label  = d$legend_label[1],
        source_tracks = d$source_track[1],
        n_points      = nrow(d),
        distance_km   = max(d$distance_km),
        elapsed_h     = d$elapsed_h[1],
        active_h      = d$active_h[1],
        break_h       = d$break_h[1],
        ascent_m      = max(d$cum_ascent_m),
        descent_m     = max(d$cum_descent_m),
        min_m         = min(
          d$ele_smooth,
          na.rm = TRUE
        ),
        max_m         = max(
          d$ele_smooth,
          na.rm = TRUE
        ),
        stringsAsFactors = FALSE
      )
    }
  )
)

days <- days[
  order(
    days$group,
    days$day_no
  ),
]

rownames(days) <- NULL


days$day_color <- NA_character_

for (g in unique(days$group)) {
  jj <- which(
    days$group == g
  )

  days$day_color[jj] <- grDevices::hcl.colors(
    length(jj),
    palette = "Dark 3"
  )
}


days$distance_start_km <- 0

for (g in unique(days$group)) {
  jj <- which(
    days$group == g
  )

  x <- days$distance_km[jj]

  days$distance_start_km[jj] <- c(
    0,
    head(
      cumsum(x),
      -1
    )
  )
}

days$distance_end_km <- days$distance_start_km +
  days$distance_km


jj <- match(
  points$day_id,
  days$day_id
)

points$day_color <- days$day_color[jj]

points$group_distance_km <- points$distance_km +
  days$distance_start_km[jj]


group_split <- split(
  days,
  days$group
)

groups <- do.call(
  rbind,
  lapply(
    group_split,
    function(d) {
      data.frame(
        group          = d$group[1],
        group_label    = d$group_label[1],
        n_days         = nrow(d),
        distance_km    = sum(d$distance_km),
        elapsed_h      = sum(d$elapsed_h),
        active_h       = sum(d$active_h),
        break_h        = sum(d$break_h),
        ascent_m       = sum(d$ascent_m),
        descent_m      = sum(d$descent_m),
        min_m          = min(d$min_m),
        max_m          = max(d$max_m),
        stringsAsFactors = FALSE
      )
    }
  )
)

rownames(groups) <- NULL


# ============================================================
# 4. CONSISTENCY CHECKS
# ============================================================

stopifnot(
  nrow(days) == nrow(manifest),
  !anyDuplicated(
    days$day_id
  ),
  setequal(
    unique(
      points$day_id
    ),
    manifest$day_id
  ),
  all(
    points$day_color ==
      days$day_color[
        match(
          points$day_id,
          days$day_id
        )
      ]
  ),
  all(
    points$group_distance_km >= 0
  ),
  all(
    abs(
      days$elapsed_h -
      days$active_h -
      days$break_h
    ) < 1e-8
  )
)

point_count <- table(
  points$day_id
)

stopifnot(
  all(
    days$n_points ==
      as.integer(
        point_count[
          days$day_id
        ]
      )
  )
)


# ============================================================
# EVERYTHING BELOW IS VISUALIZATION ONLY.
# ============================================================

make_map <- function(group) {
  d <- points[
    points$group == group,
  ]

  s <- days[
    days$group == group,
  ]

  m <- leaflet::leaflet(
    options = leaflet::leafletOptions(
      preferCanvas = TRUE
    )
  )

  m <- leaflet::addProviderTiles(
    m,
    leaflet::providers$CartoDB.Positron,
    group = "Map"
  )

  m <- leaflet::addProviderTiles(
    m,
    leaflet::providers$Esri.WorldImagery,
    group = "Satellite"
  )

  for (day in s$day_id) {
    x <- d[
      d$day_id == day,
    ]

    ss <- s[
      s$day_id == day,
    ]

    popup <- paste0(
      "<b>", ss$display_day_id, "</b>",
      "<br>", ss$date_label,
      "<br>", round(ss$distance_km, 1), " km",
      "<br>+", round(ss$ascent_m), " m",
      " / −", round(ss$descent_m), " m",
      "<br>", round(ss$active_h, 1), " active hours",
      "<br><small>Source: ",
      ss$source_tracks,
      "</small>"
    )

    # Opaque white outline.
    m <- leaflet::addPolylines(
      m,
      data = x,
      lng = ~lon,
      lat = ~lat,
      color = "white",
      weight = 6,
      opacity = 1,
      group = ss$display_day_id
    )

    # Same final day colour as Compare days.
    m <- leaflet::addPolylines(
      m,
      data = x,
      lng = ~lon,
      lat = ~lat,
      color = ss$day_color,
      weight = 3,
      opacity = 1,
      group = ss$display_day_id,
      label = ss$legend_label,
      popup = popup,
      highlightOptions = leaflet::highlightOptions(
        weight = 5,
        opacity = 1,
        bringToFront = TRUE
      )
    )
  }

  m <- leaflet::addLayersControl(
    m,
    baseGroups = c(
      "Satellite",
      "Map"
    ),
    overlayGroups = s$display_day_id,
    options = leaflet::layersControlOptions(
      collapsed = TRUE
    )
  )

  m <- leaflet::hideGroup(
    m,
    "Map"
  )

  leaflet::addScaleBar(
    m,
    position = "bottomleft"
  )
}


make_elevation_sequential <- function(group) {
  d <- points[
    points$group == group,
  ]

  s <- days[
    days$group == group,
  ]

  yr <- range(
    d$ele_smooth,
    na.rm = TRUE
  )

  ypad_low <- max(
    60,
    diff(yr) * 0.08
  )

  ypad_high <- max(
    100,
    diff(yr) * 0.12
  )

  p <- plotly::plot_ly()

  for (day in s$day_id) {
    x <- d[
      d$day_id == day,
    ]

    ss <- s[
      s$day_id == day,
    ]

    txt <- paste0(
      "<b>", ss$display_day_id, "</b>",
      "<br>", ss$date_label,
      "<br>Day distance: ",
      round(x$distance_km, 2),
      " km",
      "<br>Total distance: ",
      round(x$group_distance_km, 2),
      " km",
      "<br>Elevation: ",
      round(x$ele_smooth),
      " m"
    )

    p <- plotly::add_trace(
      p,
      x = x$group_distance_km,
      y = x$ele_smooth,
      type = "scatter",
      mode = "lines",
      name = ss$legend_label,
      text = txt,
      hoverinfo = "text",
      line = list(
        color = ss$day_color,
        width = 3
      )
    )
  }

  boundaries <- head(
    s$distance_end_km,
    -1
  )

  shapes <- lapply(
    boundaries,
    function(x) {
      list(
        type = "line",
        x0 = x,
        x1 = x,
        y0 = 0,
        y1 = 1,
        yref = "paper",
        line = list(
          width = 1,
          dash = "dot",
          color = "rgba(80,80,80,0.45)"
        )
      )
    }
  )

  plotly::layout(
    p,
    xaxis = list(
      title = "Cumulative distance across days (km)",
      zeroline = FALSE
    ),
    yaxis = list(
      title = "Elevation (m)",
      zeroline = FALSE,
      range = c(
        yr[1] - ypad_low,
        yr[2] + ypad_high
      )
    ),
    hovermode = "closest",
    showlegend = TRUE,
    legend = list(
      orientation = "v",
      x = 1.02,
      y = 1,
      xanchor = "left",
      yanchor = "top"
    ),
    shapes = shapes,
    margin = list(
      t = 35,
      r = 175,
      b = 60,
      l = 65
    )
  )
}


make_compare_days <- function(group) {
  s <- days[
    days$group == group,
  ]

  xr <- range(
    s$distance_km,
    na.rm = TRUE
  )

  yr <- range(
    s$ascent_m,
    na.rm = TRUE
  )

  xpad <- max(
    0.5,
    diff(xr) * 0.08
  )

  ypad_low <- max(
    50,
    diff(yr) * 0.10
  )

  ypad_high <- max(
    100,
    diff(yr) * 0.20
  )

  p <- plotly::plot_ly()

  for (day in s$day_id) {
    ss <- s[
      s$day_id == day,
    ]

    # Plotly marker size is diameter in pixels.
    # Diameter proportional to sqrt(active hours) makes marker area
    # proportional to active walking time. A small minimum keeps
    # partial/zero-active days visible.
    marker_size <- max(
      7,
      11 * sqrt(ss$active_h)
    )

    txt <- paste0(
      "<b>", ss$display_day_id, "</b>",
      "<br>", ss$date_label,
      "<br>Distance: ",
      round(ss$distance_km, 1),
      " km",
      "<br>Height climbed: +",
      round(ss$ascent_m),
      " m",
      "<br>Height descended: −",
      round(ss$descent_m),
      " m",
      "<br>Active: ",
      round(ss$active_h, 1),
      " h",
      "<br>Break: ",
      round(ss$break_h, 1),
      " h"
    )

    p <- plotly::add_trace(
      p,
      x = ss$distance_km,
      y = ss$ascent_m,
      type = "scatter",
      mode = "markers+text",
      name = ss$legend_label,
      text = ss$display_day_id,
      textposition = "top center",
      hovertext = txt,
      hoverinfo = "text",
      marker = list(
        size = marker_size,
        color = ss$day_color,
        opacity = 0.9,
        line = list(
          color = "white",
          width = 2
        )
      )
    )
  }

  plotly::layout(
    p,
    xaxis = list(
      title = "Distance (km)",
      zeroline = FALSE,
      range = c(
        xr[1] - xpad,
        xr[2] + xpad
      )
    ),
    yaxis = list(
      title = "Height climbed (m)",
      zeroline = FALSE,
      range = c(
        max(0, yr[1] - ypad_low),
        yr[2] + ypad_high
      )
    ),
    hovermode = "closest",
    legend = list(
      orientation = "v",
      x = 1.02,
      y = 1,
      xanchor = "left",
      yanchor = "top"
    ),
    margin = list(
      t = 35,
      r = 175,
      b = 60,
      l = 70
    )
  )
}

format_hours <- function(x) {
  h <- floor(x)
  m <- round(
    (x - h) * 60
  )

  if (m == 60) {
    h <- h + 1
    m <- 0
  }

  sprintf(
    "%d:%02d",
    h,
    m
  )
}


make_stats_table <- function(group) {
  s <- days[
    days$group == group,
  ]

  rows <- lapply(
    seq_len(nrow(s)),
    function(i) {
      htmltools::tags$tr(
        htmltools::tags$td(
          htmltools::tags$strong(
            s$display_day_id[i]
          )
        ),
        htmltools::tags$td(
          s$date_label[i]
        ),
        htmltools::tags$td(
          class = "num",
          sprintf(
            "%.1f",
            s$distance_km[i]
          )
        ),
        htmltools::tags$td(
          class = "num",
          format_hours(
            s$elapsed_h[i]
          )
        ),
        htmltools::tags$td(
          class = "num",
          format_hours(
            s$active_h[i]
          )
        ),
        htmltools::tags$td(
          class = "num",
          format_hours(
            s$break_h[i]
          )
        ),
        htmltools::tags$td(
          class = "num",
          paste0(
            "+",
            round(s$ascent_m[i])
          )
        ),
        htmltools::tags$td(
          class = "num",
          paste0(
            "−",
            round(s$descent_m[i])
          )
        ),
        htmltools::tags$td(
          class = "num",
          paste0(
            round(s$min_m[i]),
            "–",
            round(s$max_m[i])
          )
        )
      )
    }
  )

  htmltools::tags$div(
    style = "overflow-x:auto; padding:2px 4px 4px 4px;",
    htmltools::tags$table(
      class = "track-stats",
      htmltools::tags$thead(
        htmltools::tags$tr(
          htmltools::tags$th("Day"),
          htmltools::tags$th("Date"),
          htmltools::tags$th("km"),
          htmltools::tags$th("Elapsed"),
          htmltools::tags$th("Active"),
          htmltools::tags$th("Break"),
          htmltools::tags$th("↑ m"),
          htmltools::tags$th("↓ m"),
          htmltools::tags$th("Elevation m")
        )
      ),
      htmltools::tags$tbody(
        rows
      )
    )
  )
}

group_stat <- function(group, variable) {
  groups[
    groups$group == group,
    variable
  ]
}
```

2022: Abtenau
=====================================

Row {data-height=105}
-----------------------------------------------------------------------

### Distance

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "AB",
        "distance_km"
      ),
      1
    ),
    " km"
  ),
  caption = "Abtenau · total distance",
  color = "primary"
)
```

### Climbing

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "AB",
        "ascent_m"
      )
    ),
    " m"
  ),
  caption = "Abtenau · total ascent",
  color = "warning"
)
```

### Descending

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "AB",
        "descent_m"
      )
    ),
    " m"
  ),
  caption = "Abtenau · total descent",
  color = "info"
)
```

### Highest point

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "AB",
        "max_m"
      )
    ),
    " m"
  ),
  caption = "Abtenau · highest point",
  color = "success"
)
```

Row {data-height=475}
-----------------------------------------------------------------------

### Route

```{r}
make_map("AB")
```

### Elevation plot

```{r}
make_elevation_sequential("AB")
```

Row {data-height=420}
-----------------------------------------------------------------------

### Compare days · distance vs height climbed

```{r}
make_compare_days("AB")
```

### Day statistics

```{r}
make_stats_table("AB")
```

2023: GR20 Nord
=====================================

Row {data-height=105}
-----------------------------------------------------------------------

### Distance

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "JR",
        "distance_km"
      ),
      1
    ),
    " km"
  ),
  caption = "GR20 Nord · total distance",
  color = "primary"
)
```

### Climbing

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "JR",
        "ascent_m"
      )
    ),
    " m"
  ),
  caption = "GR20 Nord · total ascent",
  color = "warning"
)
```

### Descending

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "JR",
        "descent_m"
      )
    ),
    " m"
  ),
  caption = "GR20 Nord · total descent",
  color = "info"
)
```

### Highest point

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "JR",
        "max_m"
      )
    ),
    " m"
  ),
  caption = "GR20 Nord · highest point",
  color = "success"
)
```

Row {data-height=475}
-----------------------------------------------------------------------

### Route

```{r}
make_map("JR")
```

### Elevation plot

```{r}
make_elevation_sequential("JR")
```

Row {data-height=420}
-----------------------------------------------------------------------

### Compare days · distance vs height climbed

```{r}
make_compare_days("JR")
```

### Day statistics

```{r}
make_stats_table("JR")
```

2024: Galtür
=====================================

Row {data-height=105}
-----------------------------------------------------------------------

### Distance

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "GAL",
        "distance_km"
      ),
      1
    ),
    " km"
  ),
  caption = "Galtür · total distance",
  color = "primary"
)
```

### Climbing

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "GAL",
        "ascent_m"
      )
    ),
    " m"
  ),
  caption = "Galtür · total ascent",
  color = "warning"
)
```

### Descending

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "GAL",
        "descent_m"
      )
    ),
    " m"
  ),
  caption = "Galtür · total descent",
  color = "info"
)
```

### Highest point

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "GAL",
        "max_m"
      )
    ),
    " m"
  ),
  caption = "Galtür · highest point",
  color = "success"
)
```

Row {data-height=475}
-----------------------------------------------------------------------

### Route

```{r}
make_map("GAL")
```

### Elevation plot

```{r}
make_elevation_sequential("GAL")
```

Row {data-height=420}
-----------------------------------------------------------------------

### Compare days · distance vs height climbed

```{r}
make_compare_days("GAL")
```

### Day statistics

```{r}
make_stats_table("GAL")
```

2025: Écrins
=====================================

Row {data-height=105}
-----------------------------------------------------------------------

### Distance

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "ECRINS",
        "distance_km"
      ),
      1
    ),
    " km"
  ),
  caption = "Écrins · total distance",
  color = "primary"
)
```

### Climbing

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "ECRINS",
        "ascent_m"
      )
    ),
    " m"
  ),
  caption = "Écrins · total ascent",
  color = "warning"
)
```

### Descending

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "ECRINS",
        "descent_m"
      )
    ),
    " m"
  ),
  caption = "Écrins · total descent",
  color = "info"
)
```

### Highest point

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "ECRINS",
        "max_m"
      )
    ),
    " m"
  ),
  caption = "Écrins · highest point",
  color = "success"
)
```

Row {data-height=475}
-----------------------------------------------------------------------

### Route

```{r}
make_map("ECRINS")
```

### Elevation plot

```{r}
make_elevation_sequential("ECRINS")
```

Row {data-height=420}
-----------------------------------------------------------------------

### Compare days · distance vs height climbed

```{r}
make_compare_days("ECRINS")
```

### Day statistics

```{r}
make_stats_table("ECRINS")
```

2026: Flirsch
=====================================

Row {data-height=105}
-----------------------------------------------------------------------

### Distance

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "FL",
        "distance_km"
      ),
      1
    ),
    " km"
  ),
  caption = "Flirsch · total distance",
  color = "primary"
)
```

### Climbing

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "FL",
        "ascent_m"
      )
    ),
    " m"
  ),
  caption = "Flirsch · total ascent",
  color = "warning"
)
```

### Descending

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "FL",
        "descent_m"
      )
    ),
    " m"
  ),
  caption = "Flirsch · total descent",
  color = "info"
)
```

### Highest point

```{r}
flexdashboard::valueBox(
  paste0(
    round(
      group_stat(
        "FL",
        "max_m"
      )
    ),
    " m"
  ),
  caption = "Flirsch · highest point",
  color = "success"
)
```

Row {data-height=475}
-----------------------------------------------------------------------

### Route

```{r}
make_map("FL")
```

### Elevation plot

```{r}
make_elevation_sequential("FL")
```

Row {data-height=420}
-----------------------------------------------------------------------

### Compare days · distance vs height climbed

```{r}
make_compare_days("FL")
```

### Day statistics

```{r}
make_stats_table("FL")
```
